---
title: "DataFest - Data Machine Team"
author: "Sose M Casas, Meria Djirar, Anna Lai,and Xiaoxiao Wu"
date: "June 14, 2020"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, debug=TRUE)
install.packages('gtrendsR')
library (gtrendsR)
library(ggplot2)
```

## DataFest
Presented by Meria Dijirar, Jose M Cases, Anna Lai, Xiaoxiao Wu

### Indoor phyiscal activity
Exploring the trend of indoor physical activties such as workout and yoga and the will of going to a physical gym via Google Trend. 
```{r cars}
trends = gtrends(keyword = c("learn yoga at home","workout apps free", "gyms near me"), geo = "CA", time = "2020-03-10 2020-06-05")


plot(gtrendsR:: gtrends(keyword = c("learn yoga at home","workout apps free", "gyms near me"), geo = "CA", time = "2020-03-10 2020-06-05"))
head(trends)
```

Plot the graph of google search volume over time:
```{r}
time_trend=trends$interest_over_time

plot<-ggplot(data=time_trend, aes(x=date, y=hits,group=keyword,col=keyword))+
        geom_smooth(span=0.09,se=FALSE)+xlab('Time')+ylab('Number of hits')+
        theme_bw()+theme(legend.title = element_blank(),legend.position="bottom",
        legend.text=element_text(size=12))+ggtitle("Google Search Volume")
 plot

```


### Outdoor activities
Exploring the trend of searching outdoor physical activties such as going to a nearby Park by google Trend. 
```{r}
otrends = gtrends(keyword = c("Trinity Bellwoods","High Park", "parks near me"), geo = "CA", time = "2020-01-01 2020-06-05")


plot(gtrendsR:: gtrends(keyword = c("Trinity Bellwoods","High Park", "parks near me"), geo = "CA", time = "2020-01-01 2020-06-05"))
head(trends)
```


Plot the graph of google search volume over time:
```{r}
otime_trend=otrends$interest_over_time

plot<-ggplot(data=otime_trend, aes(x=date, y=hits,group=keyword,col=keyword))+
        geom_smooth(span=0.09,se=FALSE)+xlab('Time')+ylab('Number of hits')+
        theme_bw()+theme(legend.title = element_blank(),legend.position="bottom",
        legend.text=element_text(size=12))+ggtitle("Google Search Volume")
 plot

```