---
title: 'Analysis 1 - Number of Cases vs Indoor Activities in Canada (Before lockdown) '
author: "Meria"
output: word_document
---
Initially we wanted to explore and look into Canadian prior to the lockdown date of March 17th.Initially, the  mean and variance for the following is calculated:
1) the number of COVID cases in Canada
2) the number of times indoor activities 
3) the number of times outdoor activities
```{r }
library(readxl)
covid1 <- read_excel("C:/Users/Leila.H/Desktop/DataFest/covid1.xls")
View(covid1)
cases = covid1[["cases"]]
indoor_act =covid1[["indoor"]]
outdoor_act = covid1[["outdoor"]]
cases_mean = mean(cases)
ind_mean = mean(indoor_act)
out_mean = mean(outdoor_act)
cases_var = var(cases)
ind_var = var(indoor_act)
out_var = var(outdoor_act)
cases_mean 
ind_mean 
out_mean 
cases_var 
ind_var
out_var 

```


Looking at the linear correlation coeffiencent between the folllowing, one can determine the strength and ditection of the linear relationship. The sign of r indicated the direction of the linear relationship between the x variable(number of cases) and the y variable(number pf searchs on indoor and outdoor activites:
1) number of covid confirmed cases and the number of searches on indoor activities is 0.83642. In this cases,r<0 indicating y-variable(number of searches on indoor activities) tends to increases as x variable(number of cases) increases. The size of abs(r) indicates the strength of the linear relationship between y and x variable. In this case, r is near 1 indicating the the linear relationship between the variabes is strong.
2) number of covid confirmed cases and the number of searches about outdoor activities in -0.77115. Similarily here, the negative r value indicates that y-variable(number of searches on outdoor activities) tends to decreases as x increases.Also, since it is close to 1, this indicates a strong linear relationship.
```{r}
Cor_ind = cor(cases,indoor_act)
cor_out = cor(cases, outdoor_act)

Cor_ind
cor_out
```

Determining the simple linear regression when using confirmed cases as the explanatory variable and number of searches indoor and outdoor as separate response variables gives us:
1)Equation for cases vs. indoor y = 0.008246x + 9.11280
2)Equation for cases vs. outdoor y = -0.01085x + 49.81109
```{r}
ind_lm = lm(formula=indoor_act~cases)
  
out_lm = lm(formula = outdoor_act~cases)

ind_lm
out_lm

plot(ind_lm)
plot(ind_lm)

```


Statistical T-test for Indoor activites:
          y=$$B_0$$ + $$B_1$$(x) +$$e_i$$
1) Stating hypothesis: 
        Hypo_null: no linear relationship between y and x. $$B_1$$=0.
        Hypo_alter: there is a linear relationship between y and x. $$B_1$$ not equal 0.
2)$$T_o$$ for Indoor activites = 11.01
3) P - value for Indoor activites = 3.439e-15
4) Conclusion: At level of 5%, since p-value<0.05; we reject null hypothesis which states that there is not linear relationship between number of cases and number of search terms on indoor activities.
5) R^2 =0.6938 . 69% indicates the linear regression model explains most of the variation in the response variable(number of searches on indoor activites) around its mean.



Statistical T-test for Outdoor activites:
          y=$$B_0$$ + $$B_1$$(x) +$$e_i$$
1) Stating hypothesis: 
        Hypo_null: no linear relationship between y and x. $$B_1$$=0.
        Hypo_alter: there is a linear relationship between y and x. $$B_1$$ not equal 0.
2)$$T_o$$ for Outdoor activites = -8.735
3) P - value for Outdoor activites = 8.96e-12
4) Conclusion: At level of 5%, since p-value<0.05; we reject null hypothesis which states that there is not linear relationship between number of cases and number of search terms on outdoor activities.
5) R^2 = 0.5869 . 59% indicates the linear regression model explains most of the variation in the response variable(number of searches on outdoor activites) around its mean.

```{r}
summary(ind_lm)
summary(out_lm)
```




