---
title: "DataFest-Xiaoxiao Wu & Meria"
output:
  word_document: default
  pdf_document: default
---

library(gtrendsR)
library(tidyverse)
library(flexdashboard)

# Meria's Part
---
title: 'Analysis 1 - Number of Cases vs Indoor Activities in Canada (Before lockdown) '
author: "Meria"
output: word_document
---
Initially we wanted to explore and look into Canadian prior to the lockdown date of March 17th.Initially, the  mean and variance for the following is calculated:
1) the number of COVID cases in Canada
2) the number of times indoor activities 
3) the number of times outdoor activities
```{r }
library(readxl)
covid1 <- read_excel("covid1.xls")
cases = covid1[["cases"]]
indoor_act =covid1[["indoor"]]
outdoor_act = covid1[["outdoor"]]
cases_mean = mean(cases)
ind_mean = mean(indoor_act)
out_mean = mean(outdoor_act)
cases_var = var(cases)
ind_var = var(indoor_act)
out_var = var(outdoor_act)
cases_mean 
ind_mean 
out_mean 
cases_var 
ind_var
out_var 

```


Looking at the linear correlation coeffiencent between the folllowing, one can determine the strength and ditection of the linear relationship. The sign of r indicated the direction of the linear relationship between the x variable(number of cases) and the y variable(number pf searchs on indoor and outdoor activites:
1) number of covid confirmed cases and the number of searches on indoor activities is 0.83642. In this cases,r<0 indicating y-variable(number of searches on indoor activities) tends to increases as x variable(number of cases) increases. The size of abs(r) indicates the strength of the linear relationship between y and x variable. In this case, r is near 1 indicating the the linear relationship between the variabes is strong.
2) number of covid confirmed cases and the number of searches about outdoor activities in -0.77115. Similarily here, the negative r value indicates that y-variable(number of searches on outdoor activities) tends to decreases as x increases.Also, since it is close to 1, this indicates a strong linear relationship.
```{r}
Cor_ind = cor(cases,indoor_act)
cor_out = cor(cases, outdoor_act)

Cor_ind
cor_out
```

Determining the simple linear regression when using confirmed cases as the explanatory variable and number of searches indoor and outdoor as separate response variables gives us:
1)Equation for cases vs. indoor y = 0.008246x + 9.11280
2)Equation for cases vs. outdoor y = -0.01085x + 49.81109
```{r}
ind_lm = lm(formula=indoor_act~cases)
  
out_lm = lm(formula = outdoor_act~cases)

ind_lm
out_lm

plot(ind_lm)
plot(ind_lm)

```


Statistical T-test for Indoor activites:
          y=$$B_0$$ + $$B_1$$(x) +$$e_i$$
1) Stating hypothesis: 
        Hypo_null: no linear relationship between y and x. $$B_1$$=0.
        Hypo_alter: there is a linear relationship between y and x. $$B_1$$ not equal 0.
2)$$T_o$$ for Indoor activites = 11.01
3) P - value for Indoor activites = 3.439e-15
4) Conclusion: At level of 5%, since p-value<0.05; we reject null hypothesis which states that there is not linear relationship between number of cases and number of search terms on indoor activities.
5) R^2 =0.6938 . 69% indicates the linear regression model explains most of the variation in the response variable(number of searches on indoor activites) around its mean.



Statistical T-test for Outdoor activites:
          y=$$B_0$$ + $$B_1$$(x) +$$e_i$$
1) Stating hypothesis: 
        Hypo_null: no linear relationship between y and x. $$B_1$$=0.
        Hypo_alter: there is a linear relationship between y and x. $$B_1$$ not equal 0.
2)$$T_o$$ for Outdoor activites = -8.735
3) P - value for Outdoor activites = 8.96e-12
4) Conclusion: At level of 5%, since p-value<0.05; we reject null hypothesis which states that there is not linear relationship between number of cases and number of search terms on outdoor activities.
5) R^2 = 0.5869 . 59% indicates the linear regression model explains most of the variation in the response variable(number of searches on outdoor activites) around its mean.

```{r}
summary(ind_lm)
summary(out_lm)
```







##########Xiaoxiao's Part ########################

# General trend plots of search terms 
```{r,echo=T, eval=T,cache=T, message=F,warning=F}
plot(gtrendsR::gtrends(keyword = ("mental health"), geo = "CA", time = "2020-01-31 2020-06-10"))
plot(gtrendsR::gtrends(keyword = ("mental health"), geo = "CA", time = "2019-01-31 2019-06-10"))
plot(gtrendsR::gtrends(keyword = ("mental health"), geo = "CA", time = "2019-01-31 2020-06-10"))
# search hits in 2020 are generally higher than ones in 2019
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
#Shopping Stores near me VS online shopping
plot(gtrendsR::gtrends(keyword = c("stores near me + shopping mall+ shopping center","online shopping"), geo = "CA", time = "2020-01-31 2020-06-10")) #integrated index
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
# Hair Salon
plot(gtrendsR::gtrends(keyword = c("hair cut","hair salon"), geo = "CA", time = "2020-01-31 2020-06-10"))
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
#personal hygiene and health
plot(gtrendsR::gtrends(keyword = c("Mask + Hand sanitizer + Toilet paper"), time = "2020-01-01 2020-06-08")) #integrated index
plot(gtrendsR::gtrends(keyword = c("Mask","Hand sanitizer","Toilet paper"), geo = "CA", time = "2020-01-31 2020-06-10"))
# What's going on in April for the search term of "mask"?
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
plot(gtrendsR::gtrends(keyword = c("baking + home yoga + home exercise + home meditation + online shopping + hair cut", "stores near me + beach near me + shopping mall + hiking + park + hair salon"),geo = "CA", time = "2020-01-31 2020-06-10")) #integrated indoor activities v.s. outdoor activities
```
##Linear regression on periods after the lockdown
```{r,echo=T, eval=T,cache=T, message=F,warning=F}
covid19 <- as.data.frame(readxl::read_excel("/Users/Daisy/Documents/GitHub/submit-project-data-machine/COVID-19 Canada Dataset (group by month and daily) v.s. google trend.xlsx"))
head(covid19)
attach(covid19)
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
afterLockdown<- covid19[as.Date(Date,format='%d-%m-%Y') > as.Date('2020-03-17') & as.Date(Date,format='%d-%m-%Y')<= as.Date('2020-06-09'),]
head(afterLockdown)
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
cor.test(afterLockdown$indoor,afterLockdown$`Sum of numtoday`)
after_indoor_model <- lm(afterLockdown$`Sum of numtoday`~ afterLockdown$indoor)
summary(after_indoor_model)
plot(after_indoor_model)
```
1) Stating hypothesis: 
        Hypo_null: no linear relationship between y and x. $$B_1$$=0.
        Hypo_alter: there is a linear relationship between y and x. $$B_1$$ not equal 0.
3) P - value for indoor activites = 0.000537
4) Conclusion: At level of 5%, since p-value<0.05; we reject null hypothesis which states that there is not linear relationship between number of cases and number of search terms on indoor activities.
5) R^2 = 0.1262 . indicates the linear regression model explains a few of the variation in the response variable(number of searches on indoor activites) around its mean.





```{r,echo=T, eval=T,cache=T, message=F,warning=F}
cor.test(afterLockdown$outdoor,afterLockdown$`Sum of numtoday`)
after_outdoor_model <- lm(afterLockdown$`Sum of numtoday`~ afterLockdown$outdoor)
summary(after_outdoor_model)
plot(after_outdoor_model)
```
1) Stating hypothesis: 
        Hypo_null: no linear relationship between y and x. $$B_1$$=0.
        Hypo_alter: there is a linear relationship between y and x. $$B_1$$ not equal 0.
3) P - value for outdoor activites = 0.0018
4) Conclusion: At level of 5%, since p-value<0.05; we reject null hypothesis which states that there is not linear relationship between number of cases and number of search terms on outdoor activities.
5) R^2 = 0.1019  . indicates the linear regression model explains a few of the variation in the response variable(number of searches on outdoor activites) around its mean.





##Linear regression on periods after the lockdown and before the phase 1 reopen (May.14)

## Performance for Models below is not adquate
```{r,echo=T, eval=T,cache=T, message=F,warning=F}
phase1<- covid19[as.Date(Date,format='%d-%m-%Y') > as.Date('2020-03-17') & as.Date(Date,format='%d-%m-%Y')<= as.Date('2020-05-14'),]
```

```{r,echo=T, eval=T,cache=T, message=F,warning=F}
cor.test(phase1$outdoor,phase1$`Sum of numtoday`)
phase1model_outdoor <- lm(phase1$`Sum of numtoday`~ phase1$outdoor)
summary(phase1model_outdoor)
plot(phase1model_outdoor)
```
```{r,echo=T, eval=T,cache=T, message=F,warning=F}
cor.test(phase1$indoor,phase1$`Sum of numtoday`)
phase1model_indoor <- lm(phase1$`Sum of numtoday`~ phase1$indoor)
summary(phase1model_indoor)
plot(phase1model_indoor)
```

