---
title: "DataFest - Data Machine Team"
author: "Jose M Casas, Meria Djirar, Anna Lai,and Xiaoxiao Wu"
date: "June 14, 2020"
editor_options:
  chunk_output_type: inline
fontsize: 10.5pt
github-repo: DataFestUofT/submit-project-data-machine
mainfont: Palatino
site: bookdown::bookdown_site
documentclass: krantz
---


```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, debug=TRUE, tidy = TRUE)

r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)

install.packages('bookdown')
install.packages('gtrendsR')
library (gtrendsR)
library(ggplot2)

if (knitr::is_html_output()) {
  # ignore percentage widths for HTML output, unless they are used for multiple
  # figures side by side
  knitr::opts_hooks$set(out.width = function(options) {
    if (options$fig.show != 'hold' && grepl('%$', options$out.width))
      options$out.width = NULL
    options
  })
}
```


# DataFest 2020 Summer Project presented by Data Machine Team {.unnumbered}
## Name/ Title of our project {#sections .unnumbered}

## Indoor phyiscal activity {-}
Exploring the trend of indoor physical activties such as workout and yoga and the will of going to a physical gym via Google Trend. 
```{r cars}
trends = gtrends(keyword = c("learn yoga at home","workout apps free", "gyms near me"), geo = "CA", time = "2020-03-10 2020-06-05")


plot(gtrendsR:: gtrends(keyword = c("learn yoga at home","workout apps free", "gyms near me"), geo = "CA", time = "2020-03-10 2020-06-05"))
head(trends)
```

Plot the graph of google search volume over time:
```{r}
time_trend=trends$interest_over_time

plot<-ggplot(data=time_trend, aes(x=date, y=hits,group=keyword,col=keyword))+
        geom_smooth(span=0.09,se=FALSE)+xlab('Time')+ylab('Number of hits')+
        theme_bw()+theme(legend.title = element_blank(),legend.position="bottom",
        legend.text=element_text(size=12))+ggtitle("Google Search Volume")
 plot

```

## Outdoor activities {-}
Exploring the trend of searching outdoor physical activties such as going to a nearby Park by google Trend. 
```{r}
otrends = gtrends(keyword = c("Trinity Bellwoods","High Park", "parks near me"), geo = "CA", time = "2020-01-01 2020-06-05")


plot(gtrendsR:: gtrends(keyword = c("Trinity Bellwoods","High Park", "parks near me"), geo = "CA", time = "2020-01-01 2020-06-05"))
head(trends)
```


Plot the graph of google search volume over time:
```{r}
otime_trend=otrends$interest_over_time

plot<-ggplot(data=otime_trend, aes(x=date, y=hits,group=keyword,col=keyword))+
        geom_smooth(span=0.09,se=FALSE)+xlab('Time')+ylab('Number of hits')+
        theme_bw()+theme(legend.title = element_blank(),legend.position="bottom",
        legend.text=element_text(size=12))+ggtitle("Google Search Volume")
 plot

```

# Interactive elements

## Species

```{r}
library(rbokeh)
figure(width = NULL, height = NULL) %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris, color = Species)
# figure() %>%
#   ly_points(Sepal.Length, Sepal.Width, data = iris,
#     color = Species, glyph = Species)
```


Column {data-width=400}
-----------------------------------------------------------------------

## Species (Quantile)

```{r}
figure(width = NULL, height = NULL, legend_location = "top_left") %>%
  ly_quantile(Sepal.Length, group = Species, data = iris)
```

## Petal Width

```{r}
figure(width = NULL, height = NULL) %>%
  ly_points(Sepal.Length, Sepal.Width, data = iris,
    color = Petal.Width)
```